Appendix B

### 2020-03-30 contrast.Rmd
done contrasts

---
title: ""
output:
  pdf_document: default
  html_document: default
---

@@

### A contrast of meta and metafor
Contrasted meta and metafor using the classic [Cochrane bronchoconstriction dataset]((https://www.cochrane.org/CD001183/AIRWAYS_nedocromil-sodium-for-preventing-exercise-induced-bronchoconstriction)) used in many texts to demonstrate meta-analsysis. [Here is a link to these data as a tidy csv files on figshare.](https://figshare.com/articles/Meta_thinking_data_preventing_exercise-induced_bronchoconstriction/7767020)

#### Meta
```{r meta, warning=FALSE, message=FALSE}
#load primary libraries
library(tidyverse) #tidy functions to read and format data
library(meta) #meta package current version

@@

#continuous data
m1 <- metacont(Ne, Me, Se, Nc, Mc, Sc, data = data, sm = "SMD")
summary(m1)
forest(m1, layout = "JAMA")
metabias(m1)
funnel(m1)
radial(m1)

#cumulative evidence
forest(metacum(m1, pooled = "random"))

@@

### Metafor
```{r, metafor, warning=FALSE, message=FALSE}
#load primary libraries
library(tidyverse) #tidy functions to read and format data
library(metafor) #metafor package current version

>>>>

---
title: "Appendix B"
output:
  pdf_document: default
  html_document: default
---

@@

### A contrast of analyses done using the R packages meta and metafor.  
Contrasted meta and metafor using the classic [Cochrane bronchoconstriction dataset]((https://www.cochrane.org/CD001183/AIRWAYS_nedocromil-sodium-for-preventing-exercise-induced-bronchoconstriction)) used in many texts to demonstrate meta-analsysis. [Here is a link to these data as a tidy csv files on figshare.](https://figshare.com/articles/Meta_thinking_data_preventing_exercise-induced_bronchoconstriction/7767020)

#### Meta
```{r meta, warning=FALSE, message=FALSE}
#load primary libraries
library(tidyverse) #tidy functions to read and format data
library(meta) #meta package current version effective March 2020

@@

#continuous data
m1 <- metacont(Ne, Me, Se, Nc, Mc, Sc, data = data, sm = "SMD")
summary(m1)
forest(m1, layout = "JAMA")
metabias(m1)
funnel(m1)
radial(m1)
```

\newpage
### Metafor
```{r, metafor, warning=FALSE, message=FALSE}
#load primary libraries
library(tidyverse) #tidy functions to read and format data
library(metafor) #metafor package current version effective March 2020

#calculate effect sizes
data <- escalc(measure = "SMD", m1i=Me,m2i=Mc,sd1i=Se,sd2i=Sc,n1i=Ne,n2i=Nc, data=data,var.names=c("SMD","SMD_var"),digits=4) #"SMD" for the standardized mean difference.

#fit model
#m2 <- rma(yi=SMD, vi=SMD_var, mods = ~study.ID, data = data)
m2 <- rma.uni(yi=SMD, vi=SMD_var, data = data, method = "REML") #restricted maximum-likelihood estimate
summary(m2)
plot(m2)

@@
